---
title: "Insert HW Number here"
author: "Insert your name here"
date: "Insert date here"
output: html_document
---

## Load packages and data

```{r load-packages, message = FALSE}
library(fpp3)
# install and load any package necessary
```

## Questions

### Exercise 1

```{r graph_1, fig.height=3}
ggplot(data=us_gasoline)+
  geom_line(aes(x=Week, y= Barrels))
#include  the output + code
```

### Exercise 2

```{r table_!, echo = FALSE,  fig.height=3}
us_gasoline
# include only the output
```

### Exercise 3

Some math examples $$
\hat{S} = \frac{\sum_{t=1}^{T}(y_{t}-\bar{y})^3}{\hat{\sigma}^{3}}$$

My favorite math formula is $\bar{x} = \frac{\sum_{t=1}^T x_t}{T}$

```{=tex}
\begin{align*}
a & = b \\
X &\sim {\sf Norm}(10, 3) \\
5 & \le 10
\end{align*}
```
For more math examples, please check this [website](https://rpruim.github.io/s341/S19/from-class/MathinRmd.html)

### Exercise 4

Bold - **Bold**

Italic - *Italic*

blocked -`blocked`

### Exercise 5

-   ahauhauhauahua

    -   auhauhauhauhauah

    -   auhauhauhauhauah

    -   uauahauhauhauah

            - auhauhauahuahau

1.  uahuahauh
    1.  aaauhauhauha

        1.  auhauhauhaua

        2.  aauhauhauah

        3.  auhuahauhau
    
    2. uahuahaayga


Remove this text, and add your answer for Exercise 5 here.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
